A framework for adaptive width control of dense contour-parallel toolpaths in additive manufacturing

### 2019-08-28 10_applications.tex
place cite before dot

Microstructures which have layers with varying widths benefit from the prevention of under- and overfill, which will result in structures with mechanical properties more closely matching homogenized mechanical properties.
For example the result of a topology optimized structure can contain filaments of varying thickness \cite{wu2017infill} which follow a varying stress distribution (\cref{applications_bone}).
Also microstructures with homogenous thickness in the direction perpendicular to the surface of the microstructure can result in horizontal cross-sections with varying thickness;
\cref{applications_gyroid} shows how an angled gyroid structure with homogenous thickness results in heterogeneous outline shapes.
Another class of microstructures consists of homogenous patterns which employ varying thickness in order to achieve a functionally graded material.
\Cref{applications_hex} shows how the toolpathing of a hexagonal grid neatly switches between different bead counts over the volume, which prevents the jagged moves a direction parallel infill pattern would create for such a case. \cite{bates2018compressive}

>>>>

Microstructures which have layers with varying widths benefit from the prevention of under- and overfill, which will result in structures with mechanical properties more closely matching homogenized mechanical properties.
For example the result of a topology optimized structure can contain filaments of varying thickness~\cite{wu2017infill} which follow a varying stress distribution (\cref{applications_bone}).
Also microstructures with homogenous thickness in the direction perpendicular to the surface of the microstructure can result in horizontal cross-sections with varying thickness;
\cref{applications_gyroid} shows how an angled gyroid structure with homogenous thickness results in heterogeneous outline shapes.
Another class of microstructures consists of homogenous patterns which employ varying thickness in order to achieve a functionally graded material.
\Cref{applications_hex} shows how the toolpathing of a hexagonal grid neatly switches between different bead counts over the volume, which prevents the jagged moves a direction parallel infill pattern would create for such a case~\cite{bates2018compressive}.

### 2019-08-28 1_intro.tex
place cite before dot

There is a large body of literature on relating process parameters such as bead width to various mechanical properties of the end part.
The bead width has been associated with total print time, the roughness of top surfaces, printing resolution and the strength of a part, through the contact area it makes with neighboring beads. \cite{N.Turner2014,ahn2002anisotropic}
In order to accurately fabricate a part restricted to prescribed mechanical properties, we need to generate toolpaths using the corresponding process parameters as close as possible.
We therefore develop a framework which can be used to generate toolpaths which not only avoid over- and underfill, but also keep the bead width closer to the nominal bead width compared to existing techniques.
See \cref{intro_wedge}(bottom).

>>>>

There is a large body of literature on relating process parameters such as bead width to various mechanical properties of the end part.
The bead width has been associated with total print time, the roughness of top surfaces, printing resolution and the strength of a part, through the contact area it makes with neighboring beads~\cite{N.Turner2014,ahn2002anisotropic}.
In order to accurately fabricate a part restricted to prescribed mechanical properties, we need to generate toolpaths using the corresponding process parameters as close as possible.
We therefore develop a framework which can be used to generate toolpaths which not only avoid over- and underfill, but also keep the bead width closer to the nominal bead width compared to existing techniques.
See \cref{intro_wedge}(bottom).

### 2019-08-28 2_related_work.tex
'beading strategy' ==> 'beading scheme'
place cite before dot

% This paragraph explains what toolpath generation is, and the context where toolpath generation is positioned in
Given a planar contour, representing the intersection of a plane and a 3D solid object, the task is to generate a path in the domain bounded by the contour.
The nozzle is then instructed to move along the path while extruding material.
The deposited material covers the path with a certain width.
Toolpath generation is an integral part of process planning for 3D printing.
For an overview of the processing pipeline, we refer to the survey by \citeauthor{Livesu2017CGF}.~\cite{Livesu2017CGF} .
For reducing printing time and material cost, sparse infill structures such as triangular and hexagonal patterns have been used to approximate the interior of 3D shapes.
In this paper, we focus on generating toolpath that seamlessly fills the entire 2D contour.
This is sometimes called dense infill~\cite{Livesu2017CGF}.

@@

% basic toolpath strategies and their variations
Direction parallel and contour parallel are two basic toolpath strategies.
Direction parallel (or zig-zag) toolpath fills an arbitrarily shaped contour with a set of parallel, equally spaced line segments.
These parallel segments are linked at one of their extremities, to avoid frequent stop and restart.
Contour parallel toolpath typically consists of a set of equally spaced offset contours from the slice boundary.
A strategy to connect the parallel offsets was introduced in~\cite{KUIPERS2019CAD}. This approach however introduces sharp turns.
To reduce the number of sharp turns, and thereby enable faster motions, \citeauthor{Zhao2016} proposed to use Fermat spiral to cover the contour ~\cite{Zhao2016}. 
Spiral toolpaths have also been applied to machining~\cite{Held2009,Huang2017}.
One of the problems with contour parallel toolpath is that it tends to leave gaps within the slices.
This is due to the fact that the offset contour meets around the medial axis and the remaining space might not exactly match the (constant) deposition width.
To avoid problems with such gaps, hybrid approaches that combine direction and contour parallel are often used~\cite{Mcmains2000DETC,Jin2013adaptive}.
Close to the slice boundary, there are a few contour parallel curves, while in the interior there is a zig-zag pattern.
For complex shapes, the entire cross-section could be decomposed into a set of patches, and for each of them, the basic strategies can be applied~\cite{Ding2014,Jin2017RCIM}.
Alternative toolpath patterns, seen also in CNC machining, include space-filling curves~\cite{Cox1994CAD,Griffiths1994,Shaikh2016}.

% the idea, and (some of) the most related work
Our approach to reduce under- and over-filling is to deposit material with a varying width.
This allows the opportunity to locally match the nonuniform space between adjacent paths, and thus to ensure a better filling of the area.
Material extraction with a varying width can be realized by changing the extrusion rate or the nozzle travel velocity~\cite{Ertay2018,Kuipers2018}.
However, we note that the range of possible widths is not unlimited.
For instance, printing a width that is triple the nozzle diameter is challenging.
Our method to reduce underfilling is related to the work by \citeauthor{kao1998optimal}~\cite{kao1998optimal}.
Instead of uniform offsetting, they produced adaptive offsetting toolpaths based on the geometry skeleton. 
Skeleton was also used in~\cite{Jin2017RCIM} to construct a skeleton-based path for alleviating under- and over-filling in contour parallel toolpath. 
The adaptive offsetting approach by \citeauthor{kao1998optimal} handles simply geometry where there are no branches in the medial axis.
An extension was proposed by \citeauthor{Ding2016a} to handle complex shapes~\cite{Ding2016a}.
For this purpose, they made use of the medial axis to decompose the slice into a set of simple geometries.
This extension, however, inherits a problem in the original method.
From any point in the geometry skeleton to the boundary, the number of contours is constant.
Since the distance may vary considerably, this strategy leads to a toolpath with widths that may differ by a factor of two or more.
In this paper we propose an adaptive beading strategy to address this problem.

@@

% \subsection{Toolpath strategies}
% Simple Zig-Zag toolpathing strategy. \cite{mcmains2000layered}
% Patchwise Zig-Zag toolpathing strategy. \cite{Ding2014}

% Combining concentric toolpaths into continuous extrusion spirals. \cite{Held2009}

% Fractal based toolpaths. \cite{Griffiths1994, mandal2016}

@@

% \subsection{Medial axis based toolpaths}
% Adjusted Medial Axis Transform (MAT) structure for only printing the outer wall, rest area to be filled using normal infill. \cite{Moesen2011}
% \Cref{moessen}
% Problem: small grey areas which are too small for the second wall lines.

% Figuring out underfilling and overfilling arteas in concentric fill and using single squigly lines to prevent overfilling. \cite{Jin2017JMS}
% \Cref{jin}

% Using variable width lines to fit a precise amount of lines using the MAT.
% \cite{Ding2016a} apply the method from \cite{kao1998optimal}.
% \Cref{ding}

@@

% Changing extrusion rate and temperature to match a given velocity. \cite{Ertay2018}

% Changing velocity in order to change extrusion rate.
% Shortly discussed in \cite{Kuipers2018}.
% \todo{find another reference}

>>>>

% This paragraph explains what toolpath generation is, and the context where toolpath generation is positioned in
Given a planar contour, representing the intersection of a plane and a 3D solid object, the task is to generate a path in the domain bounded by the contour.
The nozzle is then instructed to move along the path while extruding material.
The deposited material covers the path with a certain width.
Toolpath generation is an integral part of process planning for 3D printing.
For an overview of the processing pipeline, we refer to the survey by \citeauthor{Livesu2017CGF}~\cite{Livesu2017CGF}.
For reducing printing time and material cost, sparse infill structures such as triangular and hexagonal patterns have been used to approximate the interior of 3D shapes.
In this paper, we focus on generating toolpath that seamlessly fills the entire 2D contour.
This is sometimes called dense infill~\cite{Livesu2017CGF}.

@@

% basic toolpath strategies and their variations
Direction parallel and contour parallel are two basic toolpath strategies.
Direction parallel (or zig-zag) toolpath fills an arbitrarily shaped contour with a set of parallel, equally spaced line segments.
These parallel segments are linked at one of their extremities, to avoid frequent stop and restart.
Contour parallel toolpath typically consists of a set of equally spaced offset contours from the slice boundary.
A strategy to connect the parallel offsets was introduced in~\cite{KUIPERS2019CAD}. This approach however introduces sharp turns.
To reduce the number of sharp turns, and thereby enable faster motions, \citeauthor{Zhao2016} proposed to use Fermat spiral to cover the contour~\cite{Zhao2016}. 
Spiral toolpaths have also been applied to machining~\cite{Held2009,Huang2017}.
One of the problems with contour parallel toolpath is that it tends to leave gaps within the slices.
This is due to the fact that the offset contour meets around the medial axis and the remaining space might not exactly match the (constant) deposition width.
To avoid problems with such gaps, hybrid approaches that combine direction and contour parallel are often used~\cite{Mcmains2000DETC,Jin2013adaptive}.
Close to the slice boundary, there are a few contour parallel curves, while in the interior there is a zig-zag pattern.
For complex shapes, the entire cross-section could be decomposed into a set of patches, and for each of them, the basic strategies can be applied~\cite{Ding2014,Jin2017RCIM}.
Alternative toolpath patterns, seen also in CNC machining, include space-filling curves~\cite{Cox1994CAD,Griffiths1994,Shaikh2016}.

% the idea, and (some of) the most related work
Our approach to reduce under- and over-filling is to deposit material with a varying width.
This allows the opportunity to locally match the nonuniform space between adjacent paths, and thus to ensure a better filling of the area.
Material extraction with a varying width can be realized by changing the extrusion rate or the nozzle travel velocity~\cite{Ertay2018,Kuipers2018}.
However, we note that the range of possible widths is not unlimited.
For instance, printing a width that is triple the nozzle diameter is challenging.
Our method to reduce underfilling is related to the work by \citeauthor{kao1998optimal}~\cite{kao1998optimal}.
Instead of uniform offsetting, they produced adaptive offsetting toolpaths based on the geometry skeleton. 
Skeleton was also used in~\cite{Jin2017RCIM} to construct a skeleton-based path for alleviating under- and over-filling in contour parallel toolpath. 
The adaptive offsetting approach by \citeauthor{kao1998optimal} handles simply geometry where there are no branches in the medial axis.
An extension was proposed by \citeauthor{Ding2016a} to handle complex shapes~\cite{Ding2016a}.
For this purpose, they made use of the medial axis to decompose the slice into a set of simple geometries.
This extension, however, inherits a problem in the original method.
From any point in the geometry skeleton to the boundary, the number of contours is constant.
Since the distance may vary considerably, this strategy leads to a toolpath with widths that may differ by a factor of two or more.
In this paper we propose an adaptive beading scheme to address this problem.

@@

% \subsection{Toolpath strategies}
% Simple Zig-Zag toolpathing strategy~\cite{mcmains2000layered}.
% Patchwise Zig-Zag toolpathing strategy~\cite{Ding2014}.

% Combining concentric toolpaths into continuous extrusion spirals~\cite{Held2009}.

% Fractal based toolpaths~\cite{Griffiths1994, mandal2016}.

@@

% \subsection{Medial axis based toolpaths}
% Adjusted Medial Axis Transform (MAT) structure for only printing the outer wall, rest area to be filled using normal infill~\cite{Moesen2011}.
% \Cref{moessen}
% Problem: small grey areas which are too small for the second wall lines.

% Figuring out underfilling and overfilling arteas in concentric fill and using single squigly lines to prevent overfilling~\cite{Jin2017JMS}.
% \Cref{jin}

% Using variable width lines to fit a precise amount of lines using the MAT.
%~\cite{Ding2016a} apply the method from~\cite{kao1998optimal}.
% \Cref{ding}

@@

% Changing extrusion rate and temperature to match a given velocity~\cite{Ertay2018}.

% Changing velocity in order to change extrusion rate.
% Shortly discussed in~\cite{Kuipers2018}.
% \todo{find another reference}

### 2019-08-28 6_validation.tex
place cite before dot

\subsection{Computational analysis}
Experiments were performed on an Intel Core i7-7500U CPU @ \SI{2.70}{\giga\hertz} using a single core and \SI{16.3}{\giga\byte} memory.
The uniform width offsetting technique was implemented using the state-of-the-art polygon offset library Clipper. \cite{johnson2014clipper}
The computation time of each slice from the data set was recorded for the uniform technique and the inward distributed scheme. 
\cref{computime} shows these computation times of each layer plotted against the vertex count of the layer.

@@

The overfill regions are calculated by adding the polygonal areas of each extrusion segment to a list.
We then add the original outline shape in reverse and perform a Vatti clipping operation \cite{Vatti2019clipping} which only keeps areas of positive winding number.
Because the reverse outline shape reduces the winding number of all extruded segments by one, only the overfill areas are left with a positive winding number.
In order to estimate the areas which are triply covered by extrusion segments, we repeat the process of adding the outline in reverse and performing Vatti's clipping operation.
These triple extrusion areas count double toward the total amount of overfill.
The resulting overfill and underfill areas are visualized for the different toolpath schemes in the top of \cref{visualized_accuracy}.

>>>>

\subsection{Computational analysis}
Experiments were performed on an Intel Core i7-7500U CPU @ \SI{2.70}{\giga\hertz} using a single core and \SI{16.3}{\giga\byte} memory.
The uniform width offsetting technique was implemented using the state-of-the-art polygon offset library Clipper~\cite{johnson2014clipper}.
The computation time of each slice from the data set was recorded for the uniform technique and the inward distributed scheme. 
\cref{computime} shows these computation times of each layer plotted against the vertex count of the layer.

@@

The overfill regions are calculated by adding the polygonal areas of each extrusion segment to a list.
We then add the original outline shape in reverse and perform a Vatti clipping operation~\cite{Vatti2019clipping} which only keeps areas of positive winding number.
Because the reverse outline shape reduces the winding number of all extruded segments by one, only the overfill areas are left with a positive winding number.
In order to estimate the areas which are triply covered by extrusion segments, we repeat the process of adding the outline in reverse and performing Vatti's clipping operation.
These triple extrusion areas count double toward the total amount of overfill.
The resulting overfill and underfill areas are visualized for the different toolpath schemes in the top of \cref{visualized_accuracy}.

### 2019-08-28 8_discussion.tex
w_* => w^*
place cite before dot

\subsection{Limitations}
In the beading schemes we discussed we set the length of the smoothed transitions to $t(n) = w_*$.
That might demand changes in cross-sectional area as high as \SI{200}{\percent} over a distance as small as the nozzle size,
which might be difficult to accurately manufacture on some hardware.
While changing the cross-sectional area of the bead could be implemented by changing the movement speed, the movement speed is also constrained by acceleration considerations around sites in the toolpath, so this approach is inherently limited.
Our schemes require a more accurate control of the volumetric flow rate (in \si{\milli\meter\cubed\per\second}).
Using a filament feeder directly mounted on the print head (a.k.a. direct drive) is certainly a large improvement over Bowden style FDM printers.,
but still some control system is required in order to accurately change the volumetric flow rate such as advance algorithms. \cite{tronvoll2019investigating}
Still inaccuracies in direct drive systems employing advance algorithms might arise due to the changes in back-pressure required by changing bead size.

>>>>

\subsection{Limitations}
In the beading schemes we discussed we set the length of the smoothed transitions to $t(n) = w^*$.
That might demand changes in cross-sectional area as high as \SI{200}{\percent} over a distance as small as the nozzle size,
which might be difficult to accurately manufacture on some hardware.
While changing the cross-sectional area of the bead could be implemented by changing the movement speed, the movement speed is also constrained by acceleration considerations around sites in the toolpath, so this approach is inherently limited.
Our schemes require a more accurate control of the volumetric flow rate (in \si{\milli\meter\cubed\per\second}).
Using a filament feeder directly mounted on the print head (a.k.a. direct drive) is certainly a large improvement over Bowden style FDM printers.,
but still some control system is required in order to accurately change the volumetric flow rate such as advance algorithms~\cite{tronvoll2019investigating}.
Still inaccuracies in direct drive systems employing advance algorithms might arise due to the changes in back-pressure required by changing bead size.
